        
        ****** Regression 1 : wage on educationXblack
        
                *** Estimate coefficients
                reg ln_wage collgrad\#\#black i.year, r
                eststo reg1_new // Storing the results in the way eststo can read.
                        
                *** Year FE indicator
                estadd local yearFE "Yes", replace 
                
                *** Get the mean of dependent variables 
                sum ln_wage if e(sample), meanonly // if e(sample) calculates estimate using the regression sample
                local mean: di \%9.2f r(mean) // Setting the mean value at 2 decimals
                estadd local dvmean `mean', replace // Getting it ready to be added to the estout command later
                
                *** Add a blank row 
                estadd local blank " ", replace
                
        
        ****** Regression 2 : hours on educationXblack
{\smallskip}
                reg hours collgrad\#\#black i.year, r
                eststo reg2_new
                
                estadd local yearFE "Yes", replace 
                sum hours if e(sample), meanonly 
                local mean: di \%9.2f r(mean) 
                estadd local dvmean `mean', replace 
                estadd local blank " ", replace
                
        
        
        ****** Regression 3 : wage on southXblack
        
                reg ln_wage south\#\#black i.year, r
                eststo reg3_new
                
                estadd local yearFE "Yes", replace 
                sum ln_wage if e(sample), meanonly 
                local mean: di \%9.2f r(mean) 
                estadd local dvmean `mean', replace 
                estadd local blank " ", replace
{\smallskip}
        
        ****** Regression 4 : hours on southXblack              
        
                reg hours south\#\#black i.year, r
                eststo reg4_new
{\smallskip}
                estadd local yearFE "Yes", replace 
                sum hours if e(sample), meanonly 
                local mean: di \%9.2f r(mean) 
                estadd local dvmean `mean', replace 
                estadd local blank " ", replace
                
                
        ***** Ouput a table
        
*** Panel A: educationXblack
                estout reg1_new reg2_new ///
                                using "$tables/regs_estout_panelA.tex", ///
                                style(tex) replace ///
                                keep(1.collgrad\#1.black) /// Keeping the estimate of interest.
                                interaction(" $\\times$ ") /// Specifying how the interaction is shown in the doc.
                                cells(b(star fmt(\%9.3f)) se(par([ ]) fmt(\%9.3f))) /// Setting how the point esitmate (b) and SE are shown.
                                starlevels(* 0.10 ** 0.05 *** 0.01) /// estout's default star levels are :* for p<.05, ** for p<.01, and *** for p<.001
                                label nonumbers prehead() eqlabels(" ", none) /// Setting column titles
                                mgroups(, none) mlabels(, none) collabels(, none) /// Setting column titles
                                stats(blank yearFE N dvmean, fmt(0) /// Adding the stats and notes on FE 
                                          labels(" " "Year FE" "Observations" "Dep. var. mean")) /// Labeling the stats and notes on FE                  
                                 postfoot(\\hline \\noalign{\lbr}\\smallskip{\rbr}) /// Writing out the lines at the bottom
                
                *** Panel B: southXblack
                estout reg3_new reg4_new ///
                                using "$tables/regs_estout_panelB.tex", ///
                                style(tex) replace ///
                                keep(1.south\#1.black) ///
                                interaction(" $\\times$ ") ///
                                cells(b(star fmt(\%9.3f)) se(par([ ]) fmt(\%9.3f))) ///
                                starlevels(* 0.10 ** 0.05 *** 0.01) ///
                                label nonumbers prehead() eqlabels(" ", none) ///
                                mgroups(, none) mlabels(, none) collabels(, none) ///
                                stats(blank yearFE N dvmean, fmt(0) ///
                                          labels(" " "Year FE" "Observations" ///
                                                         "Dep. var. mean")) ///
                                 postfoot(\\hline \\noalign{\lbr}\\smallskip{\rbr})
                                 
